Artin Group Presentations Arising from Cluster Algebras

### 2014-07-30 Paper.tex
"aaron's section edits in T"

\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}

@@

\begin{prop}
\label{cycle_types}
\cite[Proposition 2.1]{BM13} Let $\Gamma$ be a diagram of finite type. Then, a chordless cycle in the unoriented graph of $\Gamma$ is cyclically oriented in $\Gamma$. Furthermore, the unoriented graph underlying the cycle must either be a cycle such that all edges have weight 1, a square with two opposite edges of weight 2 and two opposite edges of weight 1, as pictured below, or a triangle with two edges of weight 2 and one of weight 1.

\begin{tikzpicture}[baseline=-0.5ex]
 \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
  {
    & &|[name = ul]|\circ& |[name = ur]|\circ&\\
    %
    &|[name=lu]| \circ &&&|[name=ru]| \circ \\
     & |[name = ld]|\circ&&& |[name = rd]|\circ\\
    %
    &&|[name=dl]| \circ &|[name=dr]| \circ &\\
  };
\draw
  (ul) -- node[above] {1} (ur)
  ;
  \draw
  (ul) -- node[left]{1}(lu)
  ;
  \draw
  (dr) -- node[right]{1}(rd)
  ;
  \draw
  (lu) -- node[left]{1}(ld)
  ;
  \draw
  (ru) -- node[right]{1}(rd)
  ;
  \draw
  (ur) -- node[right]{1}(ru)
  ;
  \draw
  (dl) -- node[left]{1}(ld)
  ;
  \draw[dotted]
  (dl) -- (dr)
  ; 
 \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
  {
    & |[name = ul]|\circ& |[name = ur]|\circ\\
    %
    &|[name=dl]| \circ &|[name=dr]| \circ \\
  };
\draw
  (ul) -- node[above] {1} (ur)
  ;
  \draw
  (dl) -- node[left]{2}(ul)
  ;
  \draw
  (dr) -- node[below]{1}(dl)
  ;
  \draw
  (ur) -- node[right]{2} (dr)
  ; 
   \matrix[matrix of math nodes,column sep={25pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (10,0)
  {
    && |[name = u]|\circ& \\
    %
    &|[name=dl]| \circ & &|[name=dr]| \circ \\
  };
\draw
  (u) -- node[right] {2} (dr)
  ;
  \draw
  (dl) -- node[left]{2}(u)
  ;
  \draw
  (dr) -- node[below]{1}(dl)
  ;

@@

\todo[inline]{directions of arrows within squares?}
\begin{lem}\label{lem:chordless_cycles}
Let $\Gamma$ be a diagram of finite type with $\Gamma' = \mu_k(\Gamma)$ the mutation of $\Gamma$ at vertex $k.$ Below, we list induced subdiagrams in $\Gamma$ on the left and the resulting induced subdiagrams in $\Gamma'$ with chordless cycles $C'$ on the right, after mutation at $k.$ We draw the diagrams so that $C'$ always has a clockwise cycle. Furthermore, in case $(i),$ we assume $C'$ has at least three vertices, while in case $(j),$ we assume $C'$ has at least four vertices. Every chordless cycle in $\Gamma'$ is of one of these types.

@@

    \item $C$ is an oriented cycle in $\Gamma$ with exactly one vertex in $C$ connected to $k$ by an edge of either weight 1 or 2. Then, $C'$ is the corresponding cycle in $\Gamma'.$  
\end{enumerate}

\end{lem}
\begin{proof}
See \cite[Lemma 2.5]{BM13}.
\end{proof}

@@

Recall from Section \ref{sec:main_definitions} that for $\Gamma$ a diagram of finite type, we define the associated Artin group as follows. The associated Artin group $A_\Gamma$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the following relations
\begin{itemize}
	\item[(R2)] With $m_{ij}$ as defined in ~\ref{mij_defn}, for all $i \neq j,$ we add the relations
	$\langle s_i,s_j \rangle^{m_{ij}}= \langle s_j,s_i \rangle^{m_{ij}}.$

\item[(R3)] Let $(i_0,i_1,\ldots,i_{d-1})$ be an ordered tuple such that the subgraph of $\Gamma$ on the vertices $(i_0,\ldots, i_{d-1})$ is a chordless cycle, with edges of nonzero weight from $i_k$ to $i_{k+1},$ where subscripts $k$ are taken $\pmod d.$ If $(i_0,\ldots, i_{d-1})$ is such an ordered tuple, and additionally,
\begin{enumerate}
	\item All edges in the chordless cycle are of weight 1 or 2 and the edge $i_{d-1}\rightarrow i_0$ has weight 2.
	\item All edges in the chordless cycle have weight $1.$
\end{enumerate}
we include the relation
\begin{align*}
	s_{a}s_{a+1}^{-1}s_{a+2}^{-1}\dots s_{a-2}^{-1}s_{a-1}s_{a-2}s_{a-3}\dots s_{a+1} = s_{a+1}^{-1}\dots s_{a-3}^{-1}s_{a-2}^{-1}s_{a-1}s_{a-2}\dots s_{a+1}s_{a},
\end{align*}
where subscripts are taken $\pmod d.$ We will denote this relation by r(a, a+1). 
\end{itemize}
\end{defn}

@@

\begin{rem}
We purposely include relations $(R2),(R3)$ but not $(R1)$ in order to make our relation labeling analogous to that of \cite{BM13} at the beginning of Section 3. Note that if we add the additional relation $(R1)$ as defined at the beginning of Section 3 of \cite{BM13} (namely, if we add $s_i^2 = e$ for all vertices $i$ in $\Gamma$), then we will precisely obtain the group $W_\Gamma$ as defined at the beginning of rem 3 in \cite{BM13}.
\end{rem}

\begin{rem}
Throughout the remainder of the paper, we shall frequently discuss relations on one diagram of finite type, $\Gamma,$ and another diagram of finite type $\Gamma^\prime.$ In order to distinguish the relations in these two groups, we shall refer to the relations on $\Gamma$ as $(R2),(R3)$ and the relations on $\Gamma^\prime$ as $(R2^\prime),(R3^\prime).$
\end{rem}

\begin{ex}
The relations $(R2),(R3)$ in that $\Gamma$ is a square with all edges of weight 1 are as follows:
\[\Gamma =\begin{tikzpicture}[baseline=-0.5ex]
 \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
  {
    & |[name = ul]|\circ& |[name = ur]|\circ\\
    %
    &|[name=dl]| \circ &|[name=dr]| \circ \\
  };
\draw
  (ul) -- node[above] {1} (ur)
  ;
  \draw
  (dl) -- node[left]{1}(ul)
  ;
  \draw
  (dr) -- node[below]{1}(dl)
  ;
  \draw
  (ur) -- node[right]{1} (dr)
  ;  
      \node [yshift = .4 cm,xshift = -.4 cm] at (ul){1};
   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){2};
    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
   \end{tikzpicture}\]
   \begin{enumerate}
	\item[(R2)]
	\begin{itemize}
	\item $\langle s_1,s_2 \rangle^3 = \langle s_2,s_21 \rangle^3$
	\item $\langle s_2,s_3 \rangle^3 = \langle s_3,s_2 \rangle^3$
	\item $\langle s_3,s_4 \rangle^3 = \langle s_4,s_3 \rangle^3$
	\item $\langle s_4,s_1 \rangle^3 = \langle s_1,s_4 \rangle^3$
\end{itemize} 
	\item[(R3)]
	\begin{itemize}
	\item $s_{1}s_{2}^{-1}s_{3}^{-1}s_4s_{3}s_2 = s_{2}^{-1}s_{3}^{-1}s_4s_3s_{2}s_{1}$
	\item $s_{2}s_{3}^{-1}s_{4}^{-1}s_1s_{4}s_3 = s_{3}^{-1}s_{4}^{-1}s_1s_4s_{3}s_{2}$
	\item $s_{3}s_{4}^{-1}s_{1}^{-1}s_2s_{1}s_4 = s_{4}^{-1}s_{1}^{-1}s_2s_1s_{4}s_{3}$
	\item $s_{4}s_{1}^{-1}s_{2}^{-1}s_3s_{2}s_1 = s_{1}^{-1}s_{2}^{-1}s_3s_2s_{1}s_{4}$
\end{itemize} 
\end{enumerate}
\end{ex}

\begin{rem}
Note that if $\Gamma$ is the graph associated to a Dynkin diagram, then $W_\Gamma$ as we have defined it is precisely the corresponding Artin group corresponding to that Dynkin diagram. This occurs because, in this case, we have no cycles in $\Gamma,$ and so we only have relation of the form $(R2'),$ which define the Artin group.
\end{rem}

>>>>

\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{longfig}[thm]{Figure}

@@

\begin{prop}
\label{cycle_types}
\cite[Proposition 2.1]{BM13} Let $\Gamma$ be a diagram of finite type. Then, a chordless cycle in the unoriented graph of $\Gamma$ is cyclically oriented in $\Gamma$. Furthermore, the unoriented graph underlying the cycle must either be a cycle such that all edges have weight 1, a square with two opposite edges of weight 2 and two opposite edges of weight 1, as pictured below, or a triangle with two edges of weight 2 and one of weight 1.
\\
\hspace*{-1.2cm}
\begin{tikzpicture}[baseline=-0.5ex]
 \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
  {
    & &|[name = ul]|\circ& |[name = ur]|\circ&\\
    %
    &|[name=lu]| \circ &&&|[name=ru]| \circ \\
     & |[name = ld]|\circ&&& |[name = rd]|\circ\\
    %
    &&|[name=dl]| \circ &|[name=dr]| \circ &\\
  };
\draw
  (ul) -- node[above] {1} (ur)
  ;
  \draw
  (ul) -- node[left]{1}(lu)
  ;
  \draw
  (dr) -- node[right]{1}(rd)
  ;
  \draw
  (lu) -- node[left]{1}(ld)
  ;
  \draw
  (ru) -- node[right]{1}(rd)
  ;
  \draw
  (ur) -- node[right]{1}(ru)
  ;
  \draw
  (dl) -- node[left]{1}(ld)
  ;
  \draw[dotted]
  (dl) -- (dr)
  ;
 \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (5,0)
  {
    & |[name = ul]|\circ& |[name = ur]|\circ\\
    %
    &|[name=dl]| \circ &|[name=dr]| \circ \\
  };
\draw
  (ul) -- node[above] {1} (ur)
  ;
  \draw
  (dl) -- node[left]{2}(ul)
  ;
  \draw
  (dr) -- node[below]{1}(dl)
  ;
  \draw
  (ur) -- node[right]{2} (dr)
  ;
   \matrix[matrix of math nodes,column sep={25pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (9,0)
  {
    && |[name = u]|\circ& \\
    %
    &|[name=dl]| \circ & &|[name=dr]| \circ \\
  };
\draw
  (u) -- node[right] {2} (dr)
  ;
  \draw
  (dl) -- node[left]{2}(u)
  ;
  \draw
  (dr) -- node[below]{1}(dl)
  ;

@@

\begin{longfig}
\label{fig:cycle_types}
Let $\Gamma$ be a diagram of finite type with $\Gamma' = \mu_k(\Gamma),$ the mutation of $\Gamma$ at vertex $k.$ Below, we list induced subdiagrams in $\Gamma$ on the left and the resulting induced subdiagrams in $\Gamma'$ with chordless cycles $C'$ on the right, after mutation at $k.$ We draw the diagrams so that $C'$ always has a clockwise cycle. Furthermore, in case $(i),$ we assume $C'$ has at least three vertices, while in case $(j),$ we assume $C'$ has at least four vertices.

@@

      \item
   \begin{tikzpicture}[baseline=-0.5ex]
    \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={25pt,between origins},nodes={asymmetrical rectangle}] at (8,0)
  {
    & & |[name = um]|\circ & |[name = ur]|\circ&\\
    %
    |[name = ml]|\bullet& |[name = mm]|\circ &&& |[name = mr]|\vdots \\
    %
    & & |[name = dm]|\circ & |[name = dr]|\circ&\\
  };
\draw[->]
  (mm) to node[above] {1} (ml)
  ;
  \draw[->]
  (mm) to node[above]{1}(um)
  ;
  \draw[->]
  (um) to node[above]{1}(ur)
  ;
  \draw[->]
  (ur) [bend left] to (mr)
  ;
  \draw[->]
  (mr) [bend left] to (dr)
  ;
  \draw[->]
  (dr) to node[below]{1}(dm)
  ;
  \draw[->]
  (dm) to node[below]{1}(mm)
  ;
    \node at (ml.west){$k$};
    \node at (mm.north){h};
    \node at (um.north){1};
    \node at (ur.north){2};
    \node at (dr.south){$h-2$};
    \node at (dm.south){$h-1$};
  \node [yshift = -.9 cm] at (ur){$C'$};
   \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={25pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
  {
    & & |[name = um]|\circ & |[name = ur]|\circ&\\
    %
    |[name = ml]|\bullet& |[name = mm]|\circ &&& |[name = mr]|\vdots \\
    %
    & & |[name = dm]|\circ & |[name = dr]|\circ&\\
  };
\draw[->]
  (ml) to node[above] {1} (mm)
  ;
  \draw[->]
  (mm) to node[above]{1}(um)
  ;
  \draw[->]
  (um) to node[above]{1}(ur)
  ;
  \draw[->]
  (ur) [bend left] to (mr)
  ;
  \draw[->]
  (mr) [bend left] to (dr)
  ;
  \draw[->]
  (dr) to node[below]{1}(dm)
  ;
  \draw[->]
  (dm) to node[below]{1}(mm)
  ;
    \node at (ml.west){$k$};
    \node at (mm.north){h};
    \node at (um.north){1};
    \node at (ur.north){2};
    \node at (dr.south){$h-2$};
    \node at (dm.south){$h-1$};
  \node [yshift = -.9 cm] at (ur){$C'$};
   \end{tikzpicture}
\end{enumerate}
\end{longfig}

\begin{lem}\label{lem:chordless_cycles}
\cite[Lemma 2.5]{BM13} Every chordless cycle in $\Gamma'$ is of one of the types listed in Figure ~\ref{fig:cycle_types}.
\end{lem}

@@

Recall from Section \ref{sec:main_definitions} that for $\Gamma$ a diagram of finite type, we define the associated Artin group as follows. The associated Artin group $A_\Gamma$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the following relations
\begin{itemize}
\item[(T2)] With $m_{ij}$ as defined in ~\ref{mij_defn}, for all $i \neq j,$ we add the relations
$\langle s_i,s_j \rangle^{m_{ij}}= \langle s_j,s_i \rangle^{m_{ij}}.$

\item[(T3)] Let $(i_0,i_1,\ldots,i_{d-1})$ be an ordered tuple such that the subgraph of $\Gamma$ on the vertices $(i_0,\ldots, i_{d-1})$ is a chordless cycle, with edges of nonzero weight from $i_k$ to $i_{k+1},$ where subscripts $k$ are taken $\pmod d.$ If $(i_0,\ldots, i_{d-1})$ is such an ordered tuple, and additionally,
\begin{enumerate}
\item All edges in the chordless cycle are of weight 1 or 2 and the edge $i_{d-1}\rightarrow i_0$ has weight 2.
\item All edges in the chordless cycle have weight $1.$
\end{enumerate}
we include the relation
\begin{align*}
s_{a}s_{a+1}^{-1}s_{a+2}^{-1}\dots s_{a-2}^{-1}s_{a-1}s_{a-2}s_{a-3}\dots s_{a+1} s_{a}^{-1}\dots s_{a-2}^{-1}s_{a-1}^{-1}s_{a-2}s_{a-3} \dots s_{a+1} = e
\end{align*}
where subscripts are taken $\pmod d.$ We will denote this relation by $t(a,a+1) = e$.
\end{itemize}
\end{defn}

@@

\begin{rem}
We purposely include relations $(T2),(T3)$ but not $(T1)$ in order to make our relation labeling analogous to that of \cite{BM13} at the beginning of Section 3. Note that if we add the additional relation $(T1)$ as defined at the beginning of Section 3 of \cite{BM13} (namely, if we add $s_i^2 = e$ for all vertices $i$ in $\Gamma$), then we will precisely obtain the group $W_\Gamma$ as defined at the beginning of rem 3 in \cite{BM13}.
\end{rem}

\begin{rem}
Throughout the remainder of the paper, we shall frequently discuss relations on one diagram of finite type, $\Gamma,$ and another diagram of finite type $\Gamma^\prime.$ In order to distinguish the relations in these two groups, we shall refer to the relations on $\Gamma$ as $(T2),(T3)$ and the relations on $\Gamma^\prime$ as $(T2^\prime),(T3^\prime).$
\end{rem}

\begin{ex}
The relations $(T2),(T3)$ in that $\Gamma$ is a square with all edges of weight 1 are as follows:
\[\Gamma =\begin{tikzpicture}[baseline=-0.5ex]
\matrix[matrix of math nodes,column sep={40pt,between origins},row
sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
{
& |[name = ul]|\circ& |[name = ur]|\circ\\
%
&|[name=dl]| \circ &|[name=dr]| \circ \\
};
\draw
(ul) -- node[above] {1} (ur)
;
\draw
(dl) -- node[left]{1}(ul)
;
\draw
(dr) -- node[below]{1}(dl)
;
\draw
(ur) -- node[right]{1} (dr)
;
\node [yshift = .4 cm,xshift = -.4 cm] at (ul){1};
\node [yshift = .4 cm,xshift = .4 cm] at (ur){2};
\node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
\node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
\end{tikzpicture}\]
   \begin{enumerate}
\item[(T2)]
\begin{itemize}
\item $\langle s_1,s_2 \rangle^3 = \langle s_2,s_21 \rangle^3$
\item $\langle s_2,s_3 \rangle^3 = \langle s_3,s_2 \rangle^3$
\item $\langle s_3,s_4 \rangle^3 = \langle s_4,s_3 \rangle^3$
\item $\langle s_4,s_1 \rangle^3 = \langle s_1,s_4 \rangle^3$
\end{itemize}
\item[(T3)]
\begin{itemize}
\item $s_{1}s_{2}^{-1}s_{3}^{-1}s_4s_{3}s_2s_1^{-1}s_2^{-1}s_3^{-1}s_4^{-1}s_3s_2 = e$
\item $s_{2}s_{3}^{-1}s_{4}^{-1}s_1s_{4}s_3s_2^{-1}s_3^{-1}s_4^{-1}s_1^{-1}s_4s_3 = e$
\item $s_{3}s_{4}^{-1}s_{1}^{-1}s_2s_{1}s_4s_3^{-1}s_4^{-1}s_1^{-1}s_2^{-1}s_1s_4 = e$
\item $s_{4}s_{1}^{-1}s_{2}^{-1}s_3s_{2}s_1s_4^{-1}s_1^{-1}s_2^{-1}s_3^{-1}s_2s_1 = e$
\end{itemize}
\end{enumerate}
\end{ex}

\begin{rem}
Note that if $\Gamma$ is the graph associated to a Dynkin diagram, then $W_\Gamma$ as we have defined it is precisely the corresponding Artin group corresponding to that Dynkin diagram. This occurs because, in this case, we have no cycles in $\Gamma,$ and so we only have relation of the form $(T2'),$ which define the Artin group.
\end{rem}
